Bayesian Sparsification Methods for Deep Complex-valued Networks

### 2020-06-21 paper/paper.tex
compatcified paragraph of additive noise parameterization

Simultaneously \citet{molchanov_variational_2017} proposed to use \emph{Additive Noise
Parameterization} in the factorized Gaussian $q_\theta(\omega)$ in conjunction with the
Local Reparameterization Trick. They reverted the $(\mu, \alpha)$ parameterization back
to the equivalent $(\mu, \sigma^2)$, arguing that it reduces the variance of the SGVB
\eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu$ independent
from the local output noise, injected by \eqref{eq:r-gauss-trick}. This improvement is
especially important for model pruning, since $\mu$ of relevant parameters are used
as point estimates of their values.

@@

>>>>

Simultaneously \citet{molchanov_variational_2017} proposed to use \emph{Additive Noise
Parameterization} in the factorized Gaussian $q_\theta(\omega)$ in conjunction with the
Local Reparameterization Trick. They reverted the $(\mu, \alpha)$ parameterization in
$q_\theta(\omega)$ back to $(\mu, \sigma^2)$, arguing that it reduces the variance of the
SGVB \eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu$ independent
from the local noise, injected by \eqref{eq:r-gauss-trick}. This modification is important
for pruning, since $\mu$ of relevant parameters are used as estimates of their values.

@@

% practical difference between them?
